---
title: "shinyuser"
output: github_document
---


```{r, echo = FALSE, results='asis', eval = T, eval = T, message=F, warning=F}
library(badger)
git_repo <- "systats/shinyuser"
cat(
  #badge_travis(git_repo),
  #"[![Codecov test coverage](https://codecov.io/gh/favstats/peRspective/branch/master/graph/badge.svg)](https://codecov.io/gh/favstats/peRspective?branch=master)",
	badge_code_size(git_repo),
	badge_last_commit(git_repo),
  badge_lifecycle("experimental", "blue")
)
```

This is a demonstration of how to implement user authentication directly in a shiny app. The core idea is to provide a simple, secure and modularized solution.  

Features:

1. User's credentials are saved wherever you want.
2. Clean landing page that overlays any arbitrary layout
3. Increasing security features
    + delayed login trialing (5 sec)
    + `openssl` for hourly session cookies
    + `bcrypt` for password encrypton
3. Stay logged in after refresh ([taken from calligross](https://gist.github.com/calligross/e779281b500eb93ee9e42e4d72448189)).
4. Build with [shiny.semantic](https://github.com/Appsilon/shiny.semantic) for clean design patterns
5. Tested with shinyapps.io


Minimal example of `shinyuser`

```{r, eval = F}
library(tidyverse)
library(shiny)
library(shinyjs)
library(shiny.semantic)
library(semantic.dashboard)
library(shinyuser)
library(openssl)
library(bcrypt)

ui <- function(){
  dashboardPage(
    dashboardHeader(
      inverted = T,
      login_ui("user"),
      div(class = "ui button action-button", id = "user-logout", 
        icon("power off")
      )
    ),
    dashboardSidebar(
      side = "left", size = "", inverted = T,
      sidebarMenu(
        div(class = "item",
          h4(class = "ui inverted header", "Something")
        )
      )
    ),
    dashboardBody(
      div(class = "sixteen wide column",
        "Something great content"
      )
    )
  )
}

server <- function(input, output) {
  
  users <- reactive({ 
    ### demo data frame
    dplyr::tibble(name = "admin", pw = bcrypt::hashpw("test")) %>% 
      dplyr::mutate(hash = purrr::map_chr(name, ~create_cookie(.x)))
  })
  
  user <- callModule(login_server, "user", users)

  ### content starts to load first if user is provided
  observeEvent(user(), {
    observe(print(user()))
  })
}

shinyApp(ui, server)
```

<!-- <img src = "demo.gif"> <!-- width = "80%" --> 
