---
title: "shinyuser"
output: github_document
---


```{r, echo = FALSE, results='asis', eval = T, eval = T}
library(badger)
git_repo <- "systats/shinyuser"
cat(
  #badge_travis(git_repo),
  #"[![Codecov test coverage](https://codecov.io/gh/favstats/peRspective/branch/master/graph/badge.svg)](https://codecov.io/gh/favstats/peRspective?branch=master)",
	badge_code_size(git_repo),
	badge_last_commit(git_repo),
  badge_lifecycle("experimental", "blue")
)
```

This is a demonstration of how to implement user authentication directly in a shiny app. The core idea is to provide a simple, secure and modularized solution.  

Features:

1. User's credentials are saved wherever you want.
2. Safe and secure interface.
3. Stay logged in after refresh.
2. Build with [shiny.semantic](https://github.com/Appsilon/shiny.semantic) for clean design patterns
5. Tested with shinyapps.io


Minimal example of `shinyuser`

```{r, eval = F}
library(tidyverse)
library(shiny)
library(shinyjs)
library(shiny.semantic)
library(semantic.dashboard)
library(shinyuser)

ui <- function(){
  tagList(
    dashboardPage(
      dashboardHeader(
        inverted = T,
        login_ui("user"),
        div(class = "ui button action-button", id = "user-logout", 
            icon("power off")
        )
      ),
      dashboardSidebar(
        side = "left", size = "", inverted = T,
        sidebarMenu(
          div(class = "item",
              h4(class = "ui inverted header", "Something")
          )
        )
      ),
      dashboardBody(
        div(class = "sixteen wide column",
            "Some secret content"
        )
      )
    )
  )
  
}

server <- function(input, output) {
  
  users <- reactive({ 
    tibble(name = "admin", pw  = "test")
  })
  
  user <- callModule(login_server, "user", users)
  
  observeEvent(user(), {
    observe(print(user()))
    # ... put your modules here
  })
  
}

shinyApp(ui, server)
```

 <!-- <img src = "demo.gif"> <!-- width = "80%" --> -->
 
 
 