---
title: "shinyuser"
output: github_document
---


```{r, echo = FALSE, results='asis', eval = T, eval = T}
library(badger)
git_repo <- "systats/shinyuser"
cat(
  #badge_travis(git_repo),
  #"[![Codecov test coverage](https://codecov.io/gh/favstats/peRspective/branch/master/graph/badge.svg)](https://codecov.io/gh/favstats/peRspective?branch=master)",
	badge_code_size(git_repo),
	badge_last_commit(git_repo),
  badge_lifecycle("experimental", "blue")
)
```

This is a demonstration of how to implement user authentication directly in a shiny app. The core idea is to provide a simple, secure and modularized solution.  

Features:

1. User's credentials are saved as JSON file in `data/users`
2. Easy to integrate with `shiny.info` in order to log user actions
3. Build with [shiny.semantic](https://github.com/Appsilon/shiny.semantic) for clean design patterns
3. R6 class user management 
4. Admin panel to edit user data
5. Tested with shinyapps.io


Minimal example of `shinyuser`

```{r, eval = F}
pacman::p_load(devtools, shiny, shiny.semantic, semantic.dashboard, tidyverse,
                RSQLite, shinyjs, R6)

ui <- function(){
  dashboardPage(
    dashboardHeader(
      inverted = T,
      login_ui("user", signin = F)
      # manager_ui("manager")
    ),
    dashboardSidebar(
      side = "left", size = "", inverted = T,
      sidebarMenu(
        div(class = "item",
          h4(class = "ui inverted header", "Something")
        )
      )
    ),
    dashboardBody(
      div(class = "sixteen wide column",
        #"Something great content",
        admin_ui("admin")
      )
    )
  )
}

### Initalize root user
# con <-  RSQLite::dbConnect(RSQLite::SQLite(), "data/users.db") 
# df <- tibble(username = "root", password = "test", role = "admin")
# RSQLite::dbWriteTable(con, "users", df)

server <- function(input, output) {
  
  ### Goofle sheets User authentification
  # at top: sheets_deauth()
  # at top: sheets_auth()
  # user_sheet <- "https://docs.google.com/spreadsheets/d/1ZbSSxaMuf0fV5_2exz69ahOMZH46bNwlkXSKyOjYD5w/edit?usp=sharing"
  # users <- reactive({ googlesheets4::read_sheet(user_sheet) })
  
  users <- reactive({ 
    con <-  RSQLite::dbConnect(RSQLite::SQLite(), "data/users.db") 
    con %>% 
      dplyr::tbl("users") %>% 
      as_tibble()
  })
  
  user <- callModule(login_server, "user", users)

  ### call all your modules only if a user is successfully logged in
  observeEvent(user(), {
    observe(print(user()))
    callModule(manager_server, "manager", user)
    callModule(admin_server, "admin", users)
  })
  
}

shinyApp(ui, server)
```

The app will start up with a login/sign in modal.

 <img src = "demo.gif"> <!-- width = "80%" -->